Manuscript_Github_Pchabaudi_compBerghei

### 2022-08-10 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_compBerghei.Rmd
Alter figure sizes and swap around schizont and other samples and change prop.test() to greater

bir_clade_col <- setNames(
  c('#F0E442',
    '#56B4E9',
    '#009E73',
    '#0072B2',
    '#E69F00',
    '#D55E00',
    '#CC79A7',
    '#999999',
    'black',
    'red'),
  sort(
   unique(bir_clade$clade)
  )
)

@@

ggplot(filter(chab_tpm_subfam.df.long, SorL != 'ancestral'), 
       aes(x = factor(name,
                      levels = ordering(name, 
                                        order_vector = c(times_stages_table$time, 'sch.culture'))),
           y = tpm,
           fill = subfam)) +
  geom_col(position = "fill") +
  scale_fill_manual(values = clade_col_num) +
  facet_grid(~transmission, scales = "free_x") +
  # facet_grid(transmission ~ SorL, scales = "free")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90, size = 3))
```

@@

ggplot(filter(berg_tpm_subfam.df.long, subfam != 'ancestral (n = 1)'), 
       aes(x = factor(name,
                      levels = ordering(name,
                                        order_vector = c('Ring','Troph','Schiz','Mixed'))),
           y = tpm,
           fill = subfam)) +
  geom_col(position = "fill") +
  xlab('stages') +
  scale_fill_manual(values = bir_clade_col_num) +
  facet_wrap(~experiment, scales = "free_x")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))
```

@@

bind_rows(
  lapply(str_subset(unique(chab_tpm_subfam.L.df.long$sample), 
                    pattern = 'sch.culture',
                    negate = TRUE),
         function(sample.name){
           bind_rows(
             lapply(c('rMT_sch.culture_1', 
                      'rMT_sch.culture_2', 
                      'rMT_sch.culture_3'), 
                    function(sch.cult){
                      L_forms <- c(chab_tpm_subfam.L.df.long$sum_tpm[
                        chab_tpm_subfam.L.df.long$sample == sample.name
                      ],
                      chab_tpm_subfam.L.df.long$sum_tpm[
                        chab_tpm_subfam.L.df.long$sample == sch.cult
                      ])
                      SorL_forms <- c(chab_tpm_subfam.L.df.long$sum_tpm_all[
                        chab_tpm_subfam.L.df.long$sample == sample.name
                      ],
                      chab_tpm_subfam.L.df.long$sum_tpm_all[
                        chab_tpm_subfam.L.df.long$sample == sch.cult
                      ])
                      test.stat <- prop.test(L_forms, SorL_forms,
                                             alternative = 'less')
                      data.frame(comp = paste0(sample.name, '-', sch.cult),
                                 pval = test.stat$p.value)
                    })
           )
         })
)%>% 
  mutate(padj = round(p.adjust(pval), digits = 5),
         pval = round(pval, digits = 5)) %>% 
  arrange(desc(padj))
```

@@

bind_rows(
  lapply(str_subset(unique(berg_tpm_subfam.L.df.long$sample), 
                    pattern = 'Schiz|Mixed',
                    negate = TRUE),
         function(sample.name){
           bind_rows(
             lapply(str_subset(unique(berg_tpm_subfam.L.df.long$sample), 
                               pattern = 'Schiz'), 
                    function(sch.cult){
                      L_forms <- c(berg_tpm_subfam.L.df.long$sum_tpm[
                        berg_tpm_subfam.L.df.long$sample == sample.name
                      ],
                      berg_tpm_subfam.L.df.long$sum_tpm[
                        berg_tpm_subfam.L.df.long$sample == sch.cult
                      ])
                      SorL_forms <- c(berg_tpm_subfam.L.df.long$sum_tpm_all[
                        berg_tpm_subfam.L.df.long$sample == sample.name
                      ],
                      berg_tpm_subfam.L.df.long$sum_tpm_all[
                        berg_tpm_subfam.L.df.long$sample == sch.cult
                      ])
                      test.stat <- prop.test(L_forms, SorL_forms,
                                             alternative = 'less')
                      data.frame(comp = paste0(sample.name, '-', sch.cult),
                                 pval = test.stat$p.value)
                    })
           )
         })
)%>% 
  mutate(padj = round(p.adjust(pval), digits = 5),
         pval = round(pval, digits = 5)) %>% 
  arrange(desc(padj))
```

>>>>

bir_clade_col <- setNames(
  c('#F0E442',
    '#56B4E9',
    '#009E73',
    '#00517f',
    '#E69F00',
    '#893c00',
    '#c879cc',
    '#999999',
    'black',
    'red'),
  sort(
   unique(bir_clade$clade)
  )
)

@@

( plot <- ggplot(filter(chab_tpm_subfam.df.long, 
                        SorL != 'ancestral'), 
                 aes(x = factor(name,
                                levels = ordering(name, 
                                                  order_vector = c(times_stages_table$time, 'sch.culture'))),
                     y = tpm,
                     fill = subfam)) +
    geom_col(position = "fill") +
    xlab('Stages') + ylab('TPM') +
    scale_fill_manual(values = clade_col_num[!grepl(names(clade_col_num), pattern =  'ancestral')]) +
    facet_grid(~transmission, scales = "free_x") +
    # facet_grid(transmission ~ SorL, scales = "free")+
    theme_classic()+
    theme(axis.text.x = element_text(angle = 90,
                                     hjust = 1),
          strip.text = element_text(size = 12),
          axis.text.y = element_text(size = 10),
          axis.title = element_text(size = 12))  +
  guides(fill = guide_legend(title = 'Sub-family')) )

if(global_save_var){
  ggsave(plot,
         file = 'plots/chab_subfamProp.png',
         width = 7,
         height = 8,
         units = "in")
}
```

@@

( plot <- ggplot(filter(berg_tpm_subfam.df.long, subfam != 'ancestral (n = 1)'), 
                 aes(x = factor(name,
                                levels = ordering(name,
                                                  order_vector = c('Ring','Troph','Schiz','Mixed'))),
                     y = tpm,
                     fill = subfam)) +
    geom_col(position = "fill") +
    ylab("TPM") +
    xlab('stages') +
    scale_fill_manual(values = bir_clade_col_num[!grepl(names(bir_clade_col_num), 
                                                        pattern =  'ancestral')]) +
    facet_wrap(~experiment, scales = "free_x")+
    theme_classic()+
    theme(axis.text.x = element_text(angle = 90)) )

if(global_save_var){
  ggsave(plot,
         file = 'plots/berghei_subfamProp_AsexExact.png',
         width = 7,
         height = 9,
         units = "in")
}
```

@@

bind_rows(
  lapply(str_subset(unique(chab_tpm_subfam.L.df.long$sample), 
                    pattern = 'sch.culture',
                    negate = TRUE),
         function(sample.name){
           bind_rows(
             lapply(c('rMT_sch.culture_1', 
                      'rMT_sch.culture_2', 
                      'rMT_sch.culture_3'), 
                    function(sch.cult){
                      L_forms <- c(chab_tpm_subfam.L.df.long$sum_tpm[
                        chab_tpm_subfam.L.df.long$sample == sch.cult 
                      ],
                      chab_tpm_subfam.L.df.long$sum_tpm[
                        chab_tpm_subfam.L.df.long$sample == sample.name
                      ])
                      SorL_forms <- c(chab_tpm_subfam.L.df.long$sum_tpm_all[
                        chab_tpm_subfam.L.df.long$sample == sch.cult 
                      ],
                      chab_tpm_subfam.L.df.long$sum_tpm_all[
                        chab_tpm_subfam.L.df.long$sample == sample.name
                      ])
                      test.stat <- prop.test(L_forms, SorL_forms,
                                             alternative = 'greater')
                      data.frame(comp = paste0(sample.name, '-', sch.cult),
                                 pval = test.stat$p.value)
                    })
           )
         })
)%>% 
  mutate(padj = round(p.adjust(pval), digits = 5),
         pval = round(pval, digits = 5)) %>% 
  arrange(desc(padj))
```

@@

bind_rows(
  lapply(str_subset(unique(berg_tpm_subfam.L.df.long$sample), 
                    pattern = 'Schiz|Mixed',
                    negate = TRUE),
         function(sample.name){
           bind_rows(
             lapply(str_subset(unique(berg_tpm_subfam.L.df.long$sample), 
                               pattern = 'Schiz'), 
                    function(sch.cult){
                      L_forms <- c(berg_tpm_subfam.L.df.long$sum_tpm[
                        berg_tpm_subfam.L.df.long$sample == sch.cult 
                      ],
                      berg_tpm_subfam.L.df.long$sum_tpm[
                        berg_tpm_subfam.L.df.long$sample == sample.name
                      ])
                      SorL_forms <- c(berg_tpm_subfam.L.df.long$sum_tpm_all[
                        berg_tpm_subfam.L.df.long$sample == sch.cult 
                      ],
                      berg_tpm_subfam.L.df.long$sum_tpm_all[
                        berg_tpm_subfam.L.df.long$sample == sample.name
                      ])
                      test.stat <- prop.test(L_forms, SorL_forms,
                                             alternative = 'greater')
                      data.frame(comp = paste0(sample.name, '-', sch.cult),
                                 pval = test.stat$p.value)
                    })
           )
         })
)%>% 
  mutate(padj = round(p.adjust(pval), digits = 5),
         pval = round(pval, digits = 5)) %>% 
  arrange(desc(padj))
```
